Lesson 3
========================================================

***

### What to Do First?
Notes:

What is the mission of EDA?   To let the data to surprise you. What answer do you try to answer.

The question should be simple.

Understand what variable that are most central to your questions.

Above that notation, the first thing that one should do is to come up with some interesting questions. Then, you should try your best to solve them. Using the very exact question to take your questions into apart if your questions are too big to anwswer directly.

The more clear your mind is.

The better your work is.

Leave your information and try to solve the problem with a very clear result.

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}
getwd()
list.files()
pf<-read.csv("pseudo_facebook.tsv",sep='\t')
names(pf)
```

Notes: If didn't add sep='\t, we couldn't open the data properly. Which will cease the next step.

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
# install.packages('ggplot2')
library(ggplot2)
qplot(x=dob_day,data=pf)
```

***

#### What are some things that you notice about this histogram?
Response:The first column is very high.

***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:I my audience would be lot, around 80% would see my post.

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?

Response:

#### How many of your friends do you think saw that post?
Response:90

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:80%

***

### Perceived Audience Size
Notes:It was only a quarter of the size. Draw a lot of plot.

***
### Faceting
Notes:

```{r Faceting}
qplot(x=dob_day,data=pf)+
  scale_x_discrete(breaks=1:31)+
  facet_wrap(~dob_day,ncol=3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}
qplot(
  x=friend_count,
  data=pf
)
```

#### How is this plot similar to Moira's first plot?
Response: This graph extends all the way to the 5000 mark.

***

### Limiting the Axes
Notes:

we can use xlim = c(a,b) to plot the data which range from a to b.

```{r Limiting the Axes}
qplot(
  x=friend_count,
  data=pf,
  xlim = c(0,1000)
)
```

I'd like to try another one:

```{r}
qplot(
  x=friend_count,
  data=pf)+
  scale_x_continuous(limits = c(0,1000))
```

### Exploring with Bin Width
Notes:

***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.

qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:

```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}

```

#### Who on average has more friends: men or women?
Response:

#### What's the difference between the median friend count for women and men?
Response:

#### Why would the median be a better measure than the mean?
Response:

***

### Tenure
Notes:

```{r Tenure}

```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}

```

***

### Labeling Plots
Notes:

```{r Labeling Plots}

```

***

### User Ages
Notes:

```{r User Ages}

```

#### What do you notice?
Response:

***

### The Spread of Memes
Notes:

***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}

```

***

### Likes on the Web
Notes:

```{r Likes on the Web}

```


***

### Box Plots
Notes:

```{r Box Plots}

```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}

```

***

### Box Plots, Quartiles, and Friendships
Notes:

```{r Box Plots, Quartiles, and Friendships}

```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!